---
title: 'Liligo Test 2: Paris, France Airbnb'
author: "Robert Herczeg"
date: '2017-05-14'
output:
  slidy_presentation:
      font_adjustment: -2
      footer: "Robert Herczeg"
  css: style.css
  widescreen: yes
---

```{r setup, include=FALSE, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(prophet)
library(data.table)
library(htmltools)
library(dygraphs)
library(magrittr)
library(dplyr)
library(broom)
library(tm)
library(wordcloud)
library(googleVis)
library(ggplot2)

listing_detailed <- fread("listings_detailed.csv")
# there is a problem with fread, therefoe read.csv with colClasses was used
# with colClasses it is faster to import
review_detailed <- read.csv("reviews_detailed.csv", sep = ",",
                            quote = '"',
                            colClasses = c("numeric", "numeric",
                                           "Date", "numeric",
                                           "character", "character"))
review_detailed <- data.table(review_detailed)
calendare_detailed <- fread("calendar_detailed.csv")


# multiplot script was copied from:
# http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots <- length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots / cols)),
                    ncol = cols, nrow = ceiling(numPlots / cols))
  }

 if (numPlots == 1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

```

## Data source

Data was downloaded from [Inside Airbnb](http://insideairbnb.com/get-the-data.html). 3 files were downloaded:  

* listings.csv.gz
* reviews.csv.gz
* calendar.csv.gz

  
Listings contains detailed data about the accommodations such as host name, price, different kinds of score etc.  
  
Reviews data includes the review, the date, the reviewer name etc.  
  
In the calendar data set, we can check the availabilty of given accommodation in a given day.

## Dataset - basic info  

- **48,306** hosts
- **53,920** locations
- **844,397** reviews
- There are hosts since **2008** august.
- Prices varies between 0 - 7790€. On average, an accommodation costs ~ **95€** (median - 759€).
- Reviews varies between 0 - 5510. Usually ~ **340 character long** reviews are written (median - 260).

## Room type
  

```{r room_type, echo = FALSE, warning = FALSE}
tmp_room_type <- summary(as.factor(listing_detailed$room_type))
tmp_room_type <- tmp_room_type %>% as.data.frame()
colnames(tmp_room_type) <- "count"
tmp_room_type$type <- as.factor(rownames(tmp_room_type))
```
  
There are **56,535** locations and **  `r paste(round(tmp_room_type["Entire home/apt",1] / sum(tmp_room_type$count) * 100, 2), "%", sep = "")` ** of them are entire homes/apartments.  
```{r room_type2, echo = FALSE, warning = FALSE}

ggplot(data = tmp_room_type, aes(x = type, y = count,
                                 fill = c("red", "green", "blue"))) +
    geom_bar(colour = "black", stat = "identity") +
    xlab("Room type") + ylab("Count") +
    guides(fill = FALSE)

```
  
`r paste(round(tmp_room_type["Private room",1] / sum(tmp_room_type$count) * 100, 2), "%", sep = "")` are Private rooms, while 
`r paste(round(tmp_room_type["Shared room",1] / sum(tmp_room_type$count) * 100, 2), "%", sep = "")` are Shared rooms.

## Room type - price (mean, median)
  
**Entire home/apt** are the **most expensive** compared to the other two types.
```{r room_type3, echo = FALSE, warning = FALSE}
listing_detailed$price2 <- as.numeric(gsub("\\$", "", listing_detailed$price))
tmp_price_mean <- listing_detailed[, .(meanPrice = mean(price2, na.rm = TRUE)),
                                   by = room_type]
tmp_price_median <- listing_detailed[, .(medianPrice = median(price2,
                                                              na.rm = TRUE)),
                                     by = room_type]

p_mean <- ggplot(data = tmp_price_mean,
                 aes(x = room_type, y = meanPrice,
                     fill = c("red", "green", "blue"))) +
    geom_bar(colour = "black", stat = "identity") +
    xlab("Room type - price (**mean**)") + ylab("$") +
    guides(fill = FALSE)

p_median <- ggplot(data = tmp_price_median,
                   aes(x = room_type, y = medianPrice,
                       fill = c("red", "green", "blue"))) +
    geom_bar(colour = "black", stat = "identity") +
    xlab("Room type - price (median)") + ylab("$") +
    guides(fill = FALSE)
multiplot(p_mean, p_median, cols = 2)
```

## Distribution of bedrooms
  
Most of the accommodations have **less than 2 bedrooms**. 
```{r map, echo = FALSE}
library(leaflet, quietly = TRUE)
set.seed(16)
leaflet_sample <- sample(1:dim(listing_detailed)[1], 3000)
m <- leaflet() %>%
     addTiles() %>%  # Add default OpenStreetMap map tiles
     addCircleMarkers(data = listing_detailed[leaflet_sample],
                      lng = listing_detailed$longitude[leaflet_sample],
                      lat = listing_detailed$latitude[leaflet_sample],
                      radius = 5, popup = ~htmlEscape(summary),
                      color = ~ ifelse(bedrooms >= 3, "red",
                                       ifelse(bedrooms >= 2, "blue", "yellow"))
                      #clusterOptions = markerClusterOptions()
                      )
m
```
red >= 3; blue = 2; yellow < 2  

## WordCloud

```{r wordcloud, echo = FALSE, warning = FALSE}
tmp_text <- as.character(review_detailed$comments)
tmp_text <- tolower(tmp_text)
tmp_text <- VCorpus(VectorSource(tmp_text[leaflet_sample]))
tmp_text <- tm_map(tmp_text, removePunctuation)
tmp_text <- tm_map(tmp_text, removeNumbers)
tmp_text <- tm_map(tmp_text, removeWords, stopwords("SMART"))
tmp_text <- tm_map(tmp_text, removeWords, stopwords("german"))
tmp_text <- tm_map(tmp_text, removeWords, stopwords("french"))
tmp_text <- tm_map(tmp_text, stripWhitespace)
dtm <- DocumentTermMatrix(tmp_text)
freqr <- colSums(as.matrix(dtm))

# limit words by specifying min frequency
wordcloud(names(freqr), freqr, min.freq = 80,
          colors = brewer.pal(12, "Set3"), scale = c(4, .3))

```
  
Usually, the most frequent words are **positive**. Based on 3000 random comments from reviews.

## Review tendency over time

```{r reviews_by_time, echo = FALSE, warning = FALSE}
review_detailed$count <- 1
tmp_rev <- review_detailed[, .(sum = sum(count)), by = date]
tmp_rev$date <- as.Date(tmp_rev$date)

dygraph(tmp_rev, main = "Number of reviews")  %>%
  dyRangeSelector() %>%
  dyAxis("y", label = "count") %>%
  dyOptions(axisLineWidth = 1.5, fillGraph = TRUE, drawGrid = FALSE)

```
  
The number of reviews is continuously **increasing** since the beginning.

## Review prediction - 1

The prediction shows a **growing tendency** which continues in 2018.
```{r prophet_review, echo = FALSE, warning = FALSE}
colnames(tmp_rev) <- c("ds", "y")
invisible(capture.output(m <- prophet(tmp_rev)))
future <- make_future_dataframe(m, periods = 365)
forecast <- predict(m, future)
plot(m, forecast, xlabel = "time (years)", ylabel = "number of reviews")
```
  
Based on Facebook's prophet package.

## Review prediction - 2

Simplified trends with three differents resolutions. 
```{r prophet_review2, echo = FALSE, warning = FALSE}
prophet_plot_components(m, forecast, weekly_start = 1)
```
  
**Monday** and **Sunday** are the most active days to write a review. In the yearly graph, there are two peaks one in July and one in October.
These clearly indicates that people usually visits Paris in the middle of **summer** and at the begining of **autumn**.
Based on Facebook's prophet package.

## K-mean clustering

**6** or **7** clusters were differentiated. Therefore, we can create at least 6 different segments.
```{r kmean-cluster, echo = FALSE, warning = FALSE}
tmp_review <- listing_detailed[, .(review_scores_cleanliness,
review_scores_communication, review_scores_location,
review_scores_value)]

tmp_review <- na.omit(tmp_review)
kclusts <- data.frame(k = 1:9) %>%
  group_by(k) %>%
  do(kclust = kmeans(tmp_review, .$k))

clusterings <- kclusts %>%
  group_by(k) %>%
  do(glance(.$kclust[[1]]))
ggplot(clusterings, aes(k, tot.withinss)) + geom_line() +
  xlab("number of clusters (k)") + ylab("total within sum of squares")

```
  
4 metrics were used: cleanliness, communication, location, value

## Calendaer

Two randomly choosed hosts from calendar data set and the visualization of their availability until May, 2018. 
```{r calendar, echo = FALSE, warning = FALSE, results = "asis"}
op <- options(gvis.plot.tag = "chart")
cal_1_df <- calendare_detailed[listing_id == 18054785, ]
cal_1_df$date2 <- as.Date(cal_1_df$date)
cal_1_df$price2 <- as.numeric(gsub("\\$", "", cal_1_df$price))
cal_1 <- gvisCalendar(cal_1_df, chartid = "gvis1",
                    datevar = "date2",
                    numvar = "price2",
                    options = list(
                      title = "Price",
                      height = 320,
                      calendar = "{yearLabel: { fontName: 'Times-Roman',
                               fontSize: 32, color: '#1A8763', bold: true},
                               cellSize: 10,
                               cellColor: { stroke: 'red', strokeOpacity: 0.2 },
                               focusedCellColor: {stroke:'red'}}")
)

cal_2_df <- calendare_detailed[listing_id == 5396, ]
cal_2_df$date2 <- as.Date(cal_2_df$date)
cal_2_df$price2 <- as.numeric(gsub("\\$", "", cal_2_df$price))
cal_2 <- gvisCalendar(cal_2_df, chartid = "gvis2",
                    datevar = "date2",
                    numvar = "price2",
                    options = list(
                      title = "Price",
                      height = 320,
                      calendar = "{yearLabel: { fontName: 'Times-Roman',
                               fontSize: 32, color: '#1A8763', bold: true},
                               cellSize: 10,
                               cellColor: { stroke: 'red', strokeOpacity: 0.2 },
                               focusedCellColor: {stroke:'red'}}")
)
plot(gvisMerge(cal_1, cal_2, horizontal = FALSE))
```

## Thank you for your attention!
  
